On Extending a Full-Sharing Design with Batched Scheduling

### 2015-04-15 paper.tex
performance on worst case scenarios

\documentclass{llncs}
\usepackage[utf8]{inputenc}
\usepackage[noend]{algorithmic}
\usepackage{algorithm}
\usepackage{epsfig}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{subfigure}
\usepackage{url}
\newcommand{\verbatimproperties}{\renewcommand{\baselinestretch}{0.85} \small}
%\newcommand{\tableproperties}{\centering \big}
\newcommand{\LINECOMMENT}[1]{$\triangleright$ #1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Table~\ref{tab_batched_overhead} shows the overhead ratios, when
compared with the NS design with 1 thread (running with local
scheduling), for the NS, SS and FS designs (all running TabMalloc),
when running 1, 8, 16, 24 and 32 threads with local and batched
scheduling on the five sets of benchmarks. For each design, the table
has then two columns, a column with \emph{Local} that shows results
for the local scheduling and a column with \emph{Batched} with results
for batched scheduling. The overhead results presented in both
\emph{Local} and \emph{Batched} columns use as base time the execution
times presented in the \emph{NS} column of the Table~\ref{tab_benchs}.

>>>>

\documentclass{llncs}
\usepackage[utf8]{inputenc}
\usepackage[noend]{algorithmic}
\usepackage{algorithm}
\usepackage{epsfig}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{subfigure}
\usepackage{url}
\newcommand{\verbatimproperties}{\renewcommand{\baselinestretch}{0.85} \small}
%\newcommand{\tableproperties}{\centering \big}
\newcommand{\LINECOMMENT}[1]{$\triangleright$ #1}

%\setlength{\belowcaptionskip}{-26pt}

@@

Table~\ref{tab_batched_overhead} shows the overhead ratios, when
compared with the NS design with 1 thread (running with local
scheduling), for the NS, SS and FS designs (all running TabMalloc),
when running 1, 8, 16, 24 and 32 threads with local and batched
scheduling on the five sets of benchmarks. For each design, the table
has then two columns, a column with {\bf Local} that shows results for
the local scheduling and a column with {\bf Batched} with results for
batched scheduling. The overhead results presented in both {\bf Local}
and {\bf Batched} columns use as base time the execution times
presented in the {\bf NS} column of the Table~\ref{tab_benchs}.
